---
title: "Web page presentation - Plot created with Plotly"
author: "Leena Sonpethkar"
date: "January 31, 2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown Presentation & Plotly
### Instructions
- Create a web page presentation using R Markdown that features a plot created with Plotly. - Host your webpage on either GitHub Pages, RPubs, or NeoCities. 
- Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 

### Review criteria
The rubric contains the following two questions:

- Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
- Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Submission
```{r, echo = TRUE}
library(plotly)
library(ggplot2)
library(tidyr)


data(diamonds)

dfDiamond <- diamonds %>%
              group_by(cut, color) %>%
              summarise(price = sum(price))

Sys.setenv("plotly_username"="leena-sonpethkar")
Sys.setenv("plotly_api_key"="OAPcWxwCLiUGNyeYvwGY")

pl <- plot_ly(dfDiamond, x = ~color, y = ~price, color = ~cut, type="bar") %>% 
      layout(title = "Diamond price based on Cut by Colors", xaxis=list(title="Cut"), yaxis=list(title="Price"))

pl
```

## Thanks
